\normalfont\spacedallcaps{The economic consequences of the different attitudes of a policy maker: a combined epidemiological-econometric study}

### 2021-03-02 Manuscript/manuscript.tex
PUB

know as the basic reproduction factor. This number, that is the average number of people that are infected by a single individual, describe if the epidemic is in a negative feedback (R$_{0}$<1), stationary (R$_{0}$=1), or in a positive feedback (R$_{0}$>1). As consequence if the epidemic is in a negative feedback it will be going to dissipate, if it is in positive feedback it will grow. Note that in this simple model since the parameters are not time dependent this factor is constant. If, as performed by \cite{ferrari2020modelling}, one consider time dependet parameters it will obtain a time depended parameter called $R_{t}$. For the present work we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$. The overall population $N$ was set to 60M, in order to simulate Italian population.  Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$, there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$, if the normalized infected people are more than 10 the previous threshold  she will impose, with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$, finally if the  threshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$. As we said the PM act with a certain probability, more formally stochastically: each week a random number is extracted, if this is higher than a certain threshold the relative restrictive decision is taken, otherwise not. The threshold value capture the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one. In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results. At the end of the simulation, beside the values given by the standard SIRD model (recovered and deaths), the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions.

>>>>

know as the basic reproduction factor. This number, that is the average number of people that are infected by a single individual, describe if the epidemic is in a negative feedback (R$_{0}$<1), stationary (R$_{0}$=1), or in a positive feedback (R$_{0}$>1). As consequence if the epidemic is in a negative feedback it will be going to dissipate, if it is in positive feedback it will grow. Note that in this simple model since the parameters are not time dependent this factor is constant. If, as performed by Ferrari et al. \cite{ferrari2020modelling}, time dependent parameters are considered a time depended parameter called $R_{t}$. For the present work, we limited to constant parameters: in particular we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$. The overall population $N$ was set to 60M, in order to simulate Italian population.  Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$, there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$, if the normalized infected people are more than 10 the previous threshold  she will impose, with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$, finally if the  threshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$. These attenuation parameters were adjusted taking in consideration the results of Marziano et al. in Ref. \cite{marziano2021retrospective}. As we said the PM act with a certain probability, more formally stochastically: each week a random number is extracted, if this is higher than a certain threshold the relative restrictive decision is taken, otherwise not. The threshold value capture the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one. In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results. At the end of the simulation, beside the values given by the standard SIRD model (recovered and deaths), the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions.
